---
title: "Data Prepair Template SS3"
subtitle: "Alternative Analysis to incorporate in Krill Stock Assessment Model 48.1 SubArea"
author: "Mardones, M; Watters, G.; Kinzey. D."
date:  "`r format(Sys.time(), '%d %B, %Y')`"
linkcolor: blue
output:
  html_document:
    keep_md: true
    toc: true
    toc_deep: 3
    toc_float:
      collapsed: false
      smooth_scroll: false
    theme: cosmo
    fontsize: 0.9em
    linestretch: 1.7
    html-math-method: katex
    self-contained: true
    code-tools: true
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup1}
rm(list = ls())
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE,
                      fig.align = 'center',
                      dev = 'jpeg',
                      dpi = 300)
#XQuartz is a mess, put this in your onload to default to cairo instead
options(bitmapType = "cairo") 
# (https://github.com/tidyverse/ggplot2/issues/2655)
# Lo mapas se hacen mas rapido
```

# Background

The following document intends to carry out a complementary
methodological analysis to correlate environmental variables with the
population dynamics of krill (*Euphausia superba*), in this case, with a
biological component like lengths from fishery monitoring.


# Methodology

Load data from Doug Kinzey code

Load environmental data to merge with length.


```{r echo=FALSE}
load("~/DOCAS/Data/AMLR_Length_Data/meanscaledKrillAMLR.RData")
```

Get data specific object

```{r include=FALSE}
ls()
get("haul.len.scaled")
class(haul.len.scaled)
names(haul.len.scaled)
table(haul.len.scaled[,1])
colnames(haul.len.scaled)
```
This object